---
title: "PYRA_hierfstat"
output: html_document
---

```{r}
library("adegenet")
library("hierfstat")
library("PopGenReport")
setwd("../Genetic Monitoring Info - Chapter 1/")
PYRA.genidW12<-read.genepop("./Winter 2012-13.gen")
PYRA.genidW13<-read.genepop("./Winter 2013-14.gen")
PYRA.genidW14<-read.genepop("./Winter 2014-15.gen")
PYRA.genidW15<-read.genepop("./Winter 2015-16.gen")
PYRA.genidW16<-read.genepop("./Winter 2016-17.gen")
PYRA.genidW17<-read.genepop("./Winter 2017-18.gen")
PYRA.genidW18<-read.genepop("./Winter 2018-19.gen")
PYRA.genidW19<-read.genepop("./W2019-2020.gen")
PYRA.genidS18<-read.genepop("./Summer 2018.gen")
PYRA.All.genid<-read.genepop("./Genepop_AllYears_UPDATED.gen")
PYRA.genidW18BH<-read.genepop("./W2018-BH.gen")
PYRA.genidW18CB<-read.genepop("./W2018-CB.gen")
PYRA.genidW17BH<-read.genepop("./BH2017.GEN")
PYRA.genidS19BH<-read.genepop("./S2019BH.gen")
PYRA.genidS19CB<-read.genepop("./S2019CB.gen")
PYRA.genidW19BH<-read.genepop("./BH2019.gen")
PYRA.genidW19CB<-read.genepop("./CB2019.gen")
PYRA.genidLE12<-read.genepop("./LE2012.gen")
PYRA.genidSE12<-read.genepop("./SE2012.gen")
PYRA.genidLE13<-read.genepop("./LE2013.gen")
PYRA.genidSE13<-read.genepop("./SE2013.gen")
PYRA.genidDE13<-read.genepop("./DE2013.gen")
PYRA.genidDE19<-read.genepop("./DE2019.gen")
PYRA.genidB2E19<-read.genepop("./B2E2019.gen")
PYRA.genidLE2014<-read.genepop("./LE2014.gen")
PYRA.genidSE2014<-read.genepop("./SE2014.gen")
PYRA.genidDE2014<-read.genepop("./DE2014.gen")
PYRA.genidBE2014<-read.genepop("./BE2014.gen")
PYRA.genidBE2015<-read.genepop("./BE2015.gen")
PYRA.genidLE2015<-read.genepop("./LE2015.gen")
PYRA.genidSE2015<-read.genepop("./SE2015.gen")
PYRA.genidLE2016<-read.genepop("./LE2016.gen")
PYRA.genidDE2016<-read.genepop("./DE2016.gen")
PYRA.genidBE2016<-read.genepop("./BE2016.gen")
PYRA.genidLE2017<-read.genepop("./LE2017.gen")
PYRA.genidSE2017<-read.genepop("./SE2017.gen")
PYRA.genidBE2017<-read.genepop("./BE2017.gen")
PYRA.genidDE2017<-read.genepop("./DE2017.gen")
PYRA.genidB2E2017<-read.genepop("./B2E2017.gen")
PYRA.genidB2E2018<-read.genepop("./B2E2018.gen")
PYRA.genidLE2018<-read.genepop("./LE2018.gen")
PYRA.genidSE2018<-read.genepop("./SE2018.gen")
PYRA.genidBHR2018<-read.genepop("./BHR_2018.gen")
PYRA.genidBHR2019<-read.genepop("./BHR_2019.gen")
PYRA.genidCBR2018<-read.genepop("./CBR_2018.gen")
PYRA.genidCBR2019<-read.genepop("./CBR_2019.gen")
PYRA.genidBH12018<-read.genepop("./BH1_2018.gen")
PYRA.genidBH12019<-read.genepop("./BH1_2019.gen")
PYRA.genidBH22018<-read.genepop("./BH2_2018.gen")
PYRA.genidBH22019<-read.genepop("./BH2_2019.gen")
PYRA.genidCB12018<-read.genepop("./CB1_2018.gen")
PYRA.genidCB12019<-read.genepop("./CB1_2019.gen")
PYRA.genidCB22018<-read.genepop("./CB2_2018.gen")
PYRA.genidCB22019<-read.genepop("./CB2_2019.gen")
PYRA.genidCB32019<-read.genepop("./CB3_2019.gen")

```


```{r}

PYRA.fstatW12<-genind2hierfstat(PYRA.genidW12)
PYRA.fstatW13<-genind2hierfstat(PYRA.genidW13)
PYRA.fstatW14<-genind2hierfstat(PYRA.genidW14)
PYRA.fstatW15<-genind2hierfstat(PYRA.genidW15)
PYRA.fstatW16<-genind2hierfstat(PYRA.genidW16)
PYRA.fstatW17<-genind2hierfstat(PYRA.genidW17)
PYRA.fstatW18<-genind2hierfstat(PYRA.genidW18)
PYRA.fstatW19<-genind2hierfstat(PYRA.genidW19)
PYRA.fstatS18<-genind2hierfstat(PYRA.genidS18)
PYRA.fstat_All<-genind2hierfstat(PYRA.All.genid)
PYRA.fstatW18BH<-genind2hierfstat(PYRA.genidW18BH)
PYRA.fstatW18CB<-genind2hierfstat(PYRA.genidW18CB)
PYRA.fstatW17BH<-genind2hierfstat(PYRA.genidW17BH)
PYRA.fstatS19BH<-genind2hierfstat(PYRA.genidS19BH)
PYRA.fstatS19CB<-genind2hierfstat(PYRA.genidS19CB)
PYRA.fstatW19BH<-genind2hierfstat(PYRA.genidW19BH)
PYRA.fstatW19CB<-genind2hierfstat(PYRA.genidW19CB)
PYRA.fstatLE12<-genind2hierfstat(PYRA.genidLE12)
PYRA.fstatSE12<-genind2hierfstat(PYRA.genidSE12)
PYRA.fstatLE13<-genind2hierfstat(PYRA.genidLE13)
PYRA.fstatSE13<-genind2hierfstat(PYRA.genidSE13)
PYRA.fstatDE13<-genind2hierfstat(PYRA.genidDE13)
PYRA.fstatDE19<-genind2hierfstat(PYRA.genidDE19)
PYRA.fstatB2E19<-genind2hierfstat(PYRA.genidB2E19)
PYRA.fstatLE14<-genind2hierfstat(PYRA.genidLE2014)
PYRA.fstatSE14<-genind2hierfstat(PYRA.genidSE2014)
PYRA.fstatDE14<-genind2hierfstat(PYRA.genidDE2014)
PYRA.fstatBE14<-genind2hierfstat(PYRA.genidBE2014)
PYRA.fstatLE15<-genind2hierfstat(PYRA.genidLE2015)
PYRA.fstatSE15<-genind2hierfstat(PYRA.genidSE2015)
PYRA.fstatBE15<-genind2hierfstat(PYRA.genidBE2015)
PYRA.fstatLE16<-genind2hierfstat(PYRA.genidLE2016)
PYRA.fstatDE16<-genind2hierfstat(PYRA.genidDE2016)
PYRA.fstatBE16<-genind2hierfstat(PYRA.genidBE2016)
PYRA.fstatLE17<-genind2hierfstat(PYRA.genidLE2017)
PYRA.fstatB2E17<-genind2hierfstat(PYRA.genidB2E2017)
PYRA.fstatSE17<-genind2hierfstat(PYRA.genidSE2017)
PYRA.fstatBE17<-genind2hierfstat(PYRA.genidBE2017)
PYRA.fstatDE17<-genind2hierfstat(PYRA.genidDE2017)
PYRA.fstatLE18<-genind2hierfstat(PYRA.genidLE2018)
PYRA.fstatSE18<-genind2hierfstat(PYRA.genidSE2018)
PYRA.fstatB2E18<-genind2hierfstat(PYRA.genidB2E2018)
PYRA.fstatBHR18<-genind2hierfstat(PYRA.genidBHR2018)
PYRA.fstatBHR19<-genind2hierfstat(PYRA.genidBHR2019)
PYRA.fstatCBR18<-genind2hierfstat(PYRA.genidCBR2018)
PYRA.fstatCBR19<-genind2hierfstat(PYRA.genidCBR2019)
PYRA.fstatBH118<-genind2hierfstat(PYRA.genidBH12018)
PYRA.fstatBH119<-genind2hierfstat(PYRA.genidBH12019)
PYRA.fstatBH218<-genind2hierfstat(PYRA.genidBH22018)
PYRA.fstatBH219<-genind2hierfstat(PYRA.genidBH22019)
PYRA.fstatCB118<-genind2hierfstat(PYRA.genidCB12018)
PYRA.fstatCB119<-genind2hierfstat(PYRA.genidCB12019)
PYRA.fstatCB218<-genind2hierfstat(PYRA.genidCB22018)
PYRA.fstatCB219<-genind2hierfstat(PYRA.genidCB22019)
PYRA.fstatCB319<-genind2hierfstat(PYRA.genidCB32019)

```


```{r}
pop_labels<- c(rep("W2012",45), rep("W2013",44), rep("W2014", 91), rep("W2015", 18), rep("W2016", 60), rep("W2017", 158), rep("W2018",138), rep("S2018", 54), rep("W2019",8), rep("BH2018", 3), rep("CB2018",5), rep("BH2017",5), rep("BHS2019",7), rep("CBS2019",5), rep("BH2019", 5), rep("CB2019", 10), rep("LE2012", 117), rep ("SE2012",121), rep("DE2013", 181), rep("SE2013", 221), rep("LE2013",146), rep("DE2019",14), rep("B2E2019", 38), rep("LE2014", 379), rep("SE2014",232), rep("DE2014",275), rep("BE2014",139), rep("LE2015", 232), rep("SE2015",2), rep("DE2015", 1), rep("BE2015", 457), rep ("LE2016", 93), rep ("DE2016", 11), rep("BE2016", 121), rep("LE2017", 54), rep("SE2017", 11), rep("BE2017",41), rep("DE2017", 26), rep("B2E2017",14), rep("LE2018", 23), rep("SE2018", 6), rep("B2E2018",6))
pops_separated<-seppop(PYRA.All.genid, pop=pop_labels)
names(pops_separated)
```

Winter 2012-13 Data Set
```{r}
data_W2012<-pops_separated$W2012
#data_W2012
summary_W2012<-summary(data_W2012)
summary_W2012
mean(summary_W2012$Hexp)
mean(summary_W2012$Hobs)
t.test(summary_W2012$Hobs, summary_W2012$Hexp, paired = TRUE)
#PYRA.fstatW12
AR12<-allelic.richness(PYRA.fstatW12)
#AR12
SBF12<-mean(AR12$Ar)

```

Winter 2013-14 Data Set
```{r}
data_W2013<-pops_separated$W2013
#data_W2013
summary_W2013<-summary(data_W2013)
summary_W2013
mean(summary_W2013$Hexp)
mean(summary_W2013$Hobs)
t.test(summary_W2013$Hobs, summary_W2013$Hexp, paired = TRUE)
#PYRA.fstatW13
AR13<-allelic.richness(PYRA.fstatW13)
#AR13
SBF13<-mean(AR13$Ar)
```

Winter 2014-15 Data Set
```{r}
data_W2014<-pops_separated$W2014
#data_W2014
summary_W2014<-summary(data_W2014)
summary_W2014
mean(summary_W2014$Hexp)
mean(summary_W2014$Hobs)
t.test(summary_W2014$Hobs, summary_W2014$Hexp, paired = TRUE)
#PYRA.fstatW14
AR14<-allelic.richness(PYRA.fstatW14)
#AR14
SBF14<-mean(AR14$Ar)
```

Winter 2015-16 Data Set
```{r}
data_W2015<-pops_separated$W2015
#data_W2015
summary_W2015<-summary(data_W2015)
summary_W2015
mean(summary_W2015$Hexp)
mean(summary_W2015$Hobs)
t.test(summary_W2015$Hobs, summary_W2015$Hexp, paired = TRUE)
#PYRA.fstatW15
AR15<-allelic.richness(PYRA.fstatW15)
#AR15
SBF15<-mean(AR15$Ar)
```

Winter 2016-17 Data Set
```{r}
data_W2016<-pops_separated$W2016
#data_W2016
summary_W2016<-summary(data_W2016)
summary_W2016
mean(summary_W2016$Hexp)
mean(summary_W2016$Hobs)
t.test(summary_W2016$Hobs, summary_W2016$Hexp, paired = TRUE)
#PYRA.fstatW16
AR16<-allelic.richness(PYRA.fstatW16)
#AR16
SBF_16<-mean(AR16$Ar)
```

Winter 2017-18 Data Set
```{r}
data_W2017<-pops_separated$W2017
#data_W2017
summary_W2017<-summary(data_W2017)
summary_W2017
mean(summary_W2017$Hexp)
mean(summary_W2017$Hobs)
t.test(summary_W2017$Hobs, summary_W2017$Hexp, paired = TRUE)
#PYRA.fstatW17
AR17<-allelic.richness(PYRA.fstatW17)
#AR17
SBF17<-mean(AR17$Ar)
```

Winter 2018-19 Data Set
```{r}
data_W2018<-pops_separated$W2018
#data_W2018
summary_W2018<-summary(data_W2018)
summary_W2018
mean(summary_W2018$Hexp)
mean(summary_W2018$Hobs)
t.test(summary_W2018$Hobs, summary_W2018$Hexp, paired = TRUE)
#PYRA.fstatW18
AR18<-allelic.richness(PYRA.fstatW18)
#AR18
SBF18<-mean(AR18$Ar)
```

Winter 2019-20 Data Set
```{r}
data_W2019<-pops_separated$W2019
#data_W2019
summary_W2019<-summary(data_W2019)
summary_W2019
mean(summary_W2019$Hexp)
mean(summary_W2019$Hobs)
t.test(summary_W2019$Hobs, summary_W2019$Hexp, paired = TRUE)
#PYRA.fstatW19
AR19<-allelic.richness(PYRA.fstatW19)
#AR19
SBF19<-mean(AR19$Ar)
```

Summer 2018 Data Set
```{r}
data_S2018<-pops_separated$S2018
#data_S2018
summary_S2018<-summary(data_S2018)
summary_S2018
mean(summary_S2018$Hexp)
mean(summary_S2018$Hobs)
t.test(summary_S2018$Hobs, summary_S2018$Hexp, paired = TRUE)
#PYRA.fstatS18
ARS18<-allelic.richness(PYRA.fstatS18)
#ARS18
SBF18S<-mean(ARS18$Ar)
```

Winter 2018-19 Beezley Hills Data Set
```{r}
data_BH2018<-pops_separated$BH2018
#data_BH2018
summary_BH2018<-summary(data_BH2018)
summary_BH2018
mean(summary_BH2018$Hexp)
mean(summary_BH2018$Hobs)
t.test(summary_BH2018$Hobs, summary_BH2018$Hexp, paired = TRUE)
#PYRA.fstatW18BH
ARBH18<-allelic.richness(PYRA.fstatW18BH)
#ARBH18
mean(ARBH18$Ar)
```
Winter 2018-19 Chester Butte Data set
```{r}
data_CB2018<-pops_separated$CB2018
#data_CB2018
summary_CB2018<-summary(data_CB2018)
summary_CB2018
mean(summary_CB2018$Hexp)
mean(summary_CB2018$Hobs)
t.test(summary_CB2018$Hobs, summary_CB2018$Hexp, paired = TRUE)
#PYRA.fstatW18CB
ARCB18<-allelic.richness(PYRA.fstatW18CB)
#ARCB18
mean(ARCB18$Ar)
```

WINTER 2017-18 BEEZLEY HILLS DATA SET
```{r}
data_BH2017<-pops_separated$BH2017
#data_BH2017
summary_BH2017<-summary(data_BH2017)
summary_BH2017
mean(summary_BH2017$Hexp)
mean(summary_BH2017$Hobs)
t.test(summary_BH2017$Hobs, summary_BH2017$Hexp, paired = TRUE)
#PYRA.fstatW17BH
ARBH17<-allelic.richness(PYRA.fstatW17BH)
#ARBH17
mean(ARBH17$Ar)
```
Summer 2019 Beezley Hills Data Set
```{r}
data_BHS2019<-pops_separated$BHS2019
#data_BHS2019
summary_BHS2019<-summary(data_BHS2019)
summary_BHS2019
mean(summary_BHS2019$Hexp)
mean(summary_BHS2019$Hobs)
t.test(summary_BHS2019$Hobs, summary_BHS2019$Hexp, paired = TRUE)
#PYRA.fstatS19BH
ARBHS19<-allelic.richness(PYRA.fstatS19BH)
#ARBHS19
mean(ARBHS19$Ar)
```

Summer 2019 Chester Butte Data Set
```{r}
library(hierfstat)
data_CBS2019<-pops_separated$CBS2019
#data_CBS2019
summary_CBS2019<-summary(data_CBS2019)
summary_CBS2019
mean(summary_CBS2019$Hexp)
mean(summary_CBS2019$Hobs)
t.test(summary_CBS2019$Hobs, summary_CBS2019$Hexp, paired = TRUE)
#PYRA.fstatS19CB
ARCBS19<-allelic.richness(PYRA.fstatS19CB)
#ARCBS19
mean(ARCBS19$Ar)
```
WINTER 2019-2020 BEEZLEY HILLS DATA SET
```{r}
data_BHW2019<-pops_separated$BH2019
#data_BHW2019
summary_BHW2019<-summary(data_BHW2019)
summary_BHW2019
mean(summary_BHW2019$Hexp)
mean(summary_BHW2019$Hobs)
t.test(summary_BHW2019$Hobs, summary_BHW2019$Hexp, paired = TRUE)
#PYRA.fstatW19BH
ARBH19<-allelic.richness(PYRA.fstatW19BH)
#ARBH19
mean(ARBH19$Ar)
```

WINTER 2019-2020 CHESTER BUTTE DATA SET
```{r}
data_CBW2019<-pops_separated$CB2019
#data_CBW2019
summary_CBW2019<-summary(data_CBW2019)
summary_CBW2019
mean(summary_CBW2019$Hexp)
mean(summary_CBW2019$Hobs)
t.test(summary_CBW2019$Hobs, summary_CBW2019$Hexp, paired = TRUE)
#PYRA.fstatW19CB
ARCB19<-allelic.richness(PYRA.fstatW19CB)
#ARCB19
mean(ARCB19$Ar)
```
LE2012 Data Set
```{r}
data_LE2012<-pops_separated$LE2012
#data_LE2012
summary_LE2012<-summary(data_LE2012)
summary_LE2012
mean(summary_LE2012$Hexp)
mean(summary_LE2012$Hobs)
t.test(summary_LE2012$Hobs, summary_LE2012$Hexp, paired = TRUE)
#PYRA.fstatLE12
ARLE12<-allelic.richness(PYRA.fstatLE12)
#ARLE12
mean(ARLE12$Ar)
```
SE2012 Data Set
```{r}
data_SE2012<-pops_separated$SE2012
#data_SE2012
summary_SE2012<-summary(data_SE2012)
summary_SE2012
mean(summary_SE2012$Hexp)
mean(summary_SE2012$Hobs)
t.test(summary_SE2012$Hobs, summary_SE2012$Hexp, paired = TRUE)
#PYRA.fstatSE12
ARSE12<-allelic.richness(PYRA.fstatSE12)
#ARSE12
mean(ARSE12$Ar)
```
LE2013 Data Set
```{r}
data_LE2013<-pops_separated$LE2013
#data_LE2013
summary_LE2013<-summary(data_LE2013)
summary_LE2013
mean(summary_LE2013$Hexp)
mean(summary_LE2013$Hobs)
t.test(summary_LE2013$Hobs, summary_LE2013$Hexp, paired = TRUE)
#PYRA.fstatLE13
ARLE13<-allelic.richness(PYRA.fstatLE13)
#ARLE13
mean(ARLE13$Ar)
```
SE2013 Data Set
```{r}
data_SE2013<-pops_separated$SE2013
#data_SE2013
summary_SE2013<-summary(data_SE2013)
summary_SE2013
mean(summary_SE2013$Hexp)
mean(summary_SE2013$Hobs)
t.test(summary_SE2013$Hobs, summary_SE2013$Hexp, paired = TRUE)
#PYRA.fstatSE13
ARSE13<-allelic.richness(PYRA.fstatSE13)
#ARSE13
mean(ARSE13$Ar)
```
DE2013 Data Set
```{r}
data_DE2013<-pops_separated$DE2013
#data_DE2013
summary_DE2013<-summary(data_DE2013)
summary_DE2013
mean(summary_DE2013$Hexp)
mean(summary_DE2013$Hobs)
t.test(summary_DE2013$Hobs, summary_DE2013$Hexp, paired = TRUE)
#PYRA.fstatDE13
ARDE13<-allelic.richness(PYRA.fstatDE13)
#ARDE13
mean(ARDE13$Ar)
```
DE2019 Data Set
```{r}
data_DE2019<-pops_separated$DE2019
#data_DE2019
summary_DE2019<-summary(data_DE2019)
summary_DE2019
mean(summary_DE2019$Hexp)
mean(summary_DE2019$Hobs)
t.test(summary_DE2019$Hobs, summary_DE2019$Hexp, paired = TRUE)
#PYRA.fstatDE19
ARDE19<-allelic.richness(PYRA.fstatDE19)
#ARDE19
mean(ARDE19$Ar)
```
B2E Data Set
```{r}
data_B2E2019<-pops_separated$B2E2019
#data_B2E2019
summary_B2E2019<-summary(data_B2E2019)
summary_B2E2019
mean(summary_B2E2019$Hexp)
mean(summary_B2E2019$Hobs)
t.test(summary_B2E2019$Hobs, summary_B2E2019$Hexp, paired = TRUE)
#PYRA.fstatB2E19
ARB2E19<-allelic.richness(PYRA.fstatB2E19)
#ARB2E19
mean(ARB2E19$Ar)
```
LE2014 DATA SET
```{r}
data_LE2014<-pops_separated$LE2014
#data_LE2014
summary_LE2014<-summary(data_LE2014)
summary_LE2014
mean(summary_LE2014$Hexp)
mean(summary_LE2014$Hobs)
t.test(summary_LE2014$Hobs, summary_LE2014$Hexp, paired = TRUE)
#PYRA.fstatLE2014
ARLE14<-allelic.richness(PYRA.fstatLE14)
#ARLE14
mean(ARLE14$Ar)
```
SE2014 DATA SET
```{r}
data_SE2014<-pops_separated$SE2014
#data_SE2014
summary_SE2014<-summary(data_SE2014)
summary_SE2014
mean(summary_SE2014$Hexp)
mean(summary_SE2014$Hobs)
t.test(summary_SE2014$Hobs, summary_SE2014$Hexp, paired = TRUE)
#PYRA.fstatSE2014
ARSE14<-allelic.richness(PYRA.fstatSE14)
#ARSE14
mean(ARSE14$Ar)
```
DE2014 DATA SET
```{r}
data_DE2014<-pops_separated$DE2014
#data_DE2014
summary_DE2014<-summary(data_DE2014)
summary_DE2014
mean(summary_DE2014$Hexp)
mean(summary_DE2014$Hobs)
t.test(summary_DE2014$Hobs, summary_DE2014$Hexp, paired = TRUE)
#PYRA.fstatDE2014
ARDE14<-allelic.richness(PYRA.fstatDE14)
#ARDE14
mean(ARDE14$Ar)
```
BE2014 DATA SET
```{r}
data_BE2014<-pops_separated$BE2014
#data_BE2014
summary_BE2014<-summary(data_BE2014)
summary_BE2014
mean(summary_BE2014$Hexp)
mean(summary_BE2014$Hobs)
t.test(summary_BE2014$Hobs, summary_BE2014$Hexp, paired = TRUE)
#PYRA.fstatBE2014
ARBE14<-allelic.richness(PYRA.fstatBE14)
#ARBE14
mean(ARBE14$Ar)
```
LE2015 DATA SET
```{r}
data_LE2015<-pops_separated$LE2015
#data_LE2015
summary_LE2015<-summary(data_LE2015)
summary_LE2015
mean(summary_LE2015$Hexp)
mean(summary_LE2015$Hobs)
t.test(summary_LE2015$Hobs, summary_LE2015$Hexp, paired = TRUE)
#PYRA.fstatLE2015
ARLE15<-allelic.richness(PYRA.fstatLE15)
#ARLE15
mean(ARLE15$Ar)
```
SE2015 DATA SET
```{r}
data_SE2015<-pops_separated$SE2015
#data_SE2015
summary_SE2015<-summary(data_SE2015)
summary_SE2015
mean(summary_SE2015$Hexp)
mean(summary_SE2015$Hobs)
t.test(summary_SE2015$Hobs, summary_SE2015$Hexp, paired = TRUE)
#PYRA.fstatSE2015
ARSE15<-allelic.richness(PYRA.fstatSE15)
#ARSE15
mean(ARSE15$Ar)
```

BE2015 DATA SET
```{r}
data_BE2015<-pops_separated$BE2015
#data_BE2015
summary_BE2015<-summary(data_BE2015)
summary_BE2015
mean(summary_BE2015$Hexp)
mean(summary_BE2015$Hobs)
t.test(summary_BE2015$Hobs, summary_BE2015$Hexp, paired = TRUE)
#PYRA.fstatBE2015
ARBE15<-allelic.richness(PYRA.fstatBE15)
#ARBE15
mean(ARBE15$Ar)
```

LE2016 DATA SET

```{r}
data_LE2016<-pops_separated$LE2016
#data_LE2016
summary_LE2016<-summary(data_LE2016)
summary_LE2016
mean(summary_LE2016$Hexp)
mean(summary_LE2016$Hobs)
t.test(summary_LE2016$Hobs, summary_LE2016$Hexp, paired = TRUE)
#PYRA.fstatLE2016
ARLE16<-allelic.richness(PYRA.fstatLE16)
#ARLE16
mean(ARLE16$Ar)
```

DE2016 DATA SET
```{r}
data_DE2016<-pops_separated$DE2016
#data_DE2016
summary_DE2016<-summary(data_DE2016)
summary_DE2016
mean(summary_DE2016$Hexp)
mean(summary_DE2016$Hobs)
t.test(summary_DE2016$Hobs, summary_DE2016$Hexp, paired = TRUE)
#PYRA.fstatDE2016
ARDE16<-allelic.richness(PYRA.fstatDE16)
#ARDE16
mean(ARDE16$Ar)
```

BE2016 DATA SET
```{r}
data_BE2016<-pops_separated$BE2016
#data_BE2016
summary_BE2016<-summary(data_BE2016)
summary_BE2016
mean(summary_BE2016$Hexp)
mean(summary_BE2016$Hobs)
t.test(summary_BE2016$Hobs, summary_BE2016$Hexp, paired = TRUE)
#PYRA.fstatBE2016
ARBE16<-allelic.richness(PYRA.fstatBE16)
#ARBE16
mean(ARBE16$Ar)
```
LE2017 DATA SET
```{r}
data_LE2017<-pops_separated$LE2017
#data_LE2017
summary_LE2017<-summary(data_LE2017)
summary_LE2017
mean(summary_LE2017$Hexp)
mean(summary_LE2017$Hobs)
t.test(summary_LE2017$Hobs, summary_LE2017$Hexp, paired = TRUE)
#PYRA.fstatLE2017
ARLE17<-allelic.richness(PYRA.fstatLE17)
#ARLE17
mean(ARLE17$Ar)
```
SE2017 DATA SET
```{r}
data_SE2017<-pops_separated$SE2017
#data_SE2017
summary_SE2017<-summary(data_SE2017)
summary_SE2017
mean(summary_SE2017$Hexp)
mean(summary_SE2017$Hobs)
t.test(summary_SE2017$Hobs, summary_SE2017$Hexp, paired = TRUE)
#PYRA.fstatSE2017
ARSE17<-allelic.richness(PYRA.fstatSE17)
#ARSE17
mean(ARSE17$Ar)
```
DE2017 DATA SET
```{r}
data_DE2017<-pops_separated$DE2017
#data_DE2017
summary_DE2017<-summary(data_DE2017)
summary_DE2017
mean(summary_DE2017$Hexp)
mean(summary_DE2017$Hobs)
t.test(summary_DE2017$Hobs, summary_DE2017$Hexp, paired = TRUE)
#PYRA.fstatDE2017
ARDE17<-allelic.richness(PYRA.fstatDE17)
#ARDE17
mean(ARDE17$Ar)
```
BE2017 DATA SET
```{r}
data_BE2017<-pops_separated$BE2017
#data_BE2017
summary_BE2017<-summary(data_BE2017)
summary_BE2017
mean(summary_BE2017$Hexp)
mean(summary_BE2017$Hobs)
t.test(summary_BE2017$Hobs, summary_BE2017$Hexp, paired = TRUE)
#PYRA.fstatBE2017
ARBE17<-allelic.richness(PYRA.fstatBE17)
#ARBE17
mean(ARBE17$Ar)
```
B2E2017 DATA SET
```{r}
data_B2E2017<-pops_separated$B2E2017
#data_B2E2017
summary_B2E2017<-summary(data_B2E2017)
summary_B2E2017
mean(summary_B2E2017$Hexp)
mean(summary_B2E2017$Hobs)
t.test(summary_B2E2017$Hobs, summary_B2E2017$Hexp, paired = TRUE)
#PYRA.fstatB2E2017
ARB2E17<-allelic.richness(PYRA.fstatB2E17)
#ARB2E17
mean(ARB2E17$Ar)
```
B2E2018 DATA SET
```{r}
data_B2E2018<-pops_separated$B2E2018
#data_B2E2018
summary_B2E2018<-summary(data_B2E2018)
summary_B2E2018
mean(summary_B2E2018$Hexp)
mean(summary_B2E2018$Hobs)
t.test(summary_B2E2018$Hobs, summary_B2E2018$Hexp, paired = TRUE)
#PYRA.fstatB2E2018
ARB2E18<-allelic.richness(PYRA.fstatB2E18)
#ARB2E18
mean(ARB2E18$Ar)
```
LE2018 DATA SET
```{r}
data_LE2018<-pops_separated$LE2018
#data_LE2018
summary_LE2018<-summary(data_LE2018)
summary_LE2018
mean(summary_LE2018$Hexp)
mean(summary_LE2018$Hobs)
t.test(summary_LE2018$Hobs, summary_LE2018$Hexp, paired = TRUE)
#PYRA.fstatLE2018
ARLE18<-allelic.richness(PYRA.fstatLE18)
#ARLE18
mean(ARLE18$Ar)
```
SE2018 DATA SET
```{r}
data_SE2018<-pops_separated$SE2018
#data_SE2018
summary_SE2018<-summary(data_SE2018)
summary_SE2018
mean(summary_SE2018$Hexp)
mean(summary_SE2018$Hobs)
t.test(summary_SE2018$Hobs, summary_SE2018$Hexp, paired = TRUE)
#PYRA.fstatSE2018
ARSE18<-allelic.richness(PYRA.fstatSE18)
#ARSE18
mean(ARSE18$Ar)
```

```{r}
t.test(AR12$Ar,AR13$Ar, paired = FALSE)
t.test(AR13$Ar,AR14$Ar, paired = FALSE)
t.test(AR14$Ar,AR15$Ar, paired = FALSE)
t.test(AR15$Ar,AR16$Ar, paired = FALSE)
t.test(AR16$Ar,AR17$Ar, paired = FALSE)
t.test(AR17$Ar,AR18$Ar, paired = FALSE)
t.test(AR17$Ar,ARS18$Ar, paired = FALSE)
t.test(ARS18$Ar,AR18$Ar, paired = FALSE)
t.test(AR18$Ar,AR19$Ar, paired = FALSE)

```
```{r}
t.test(ARBH17$Ar, ARBH18$Ar, paired = FALSE)
t.test(ARBH18$Ar, ARBHS19$Ar, paired = FALSE)
t.test(ARBHS19$Ar, ARBH19$Ar, paired = FALSE)
t.test(ARBH18$Ar, ARBH19$Ar, paired = FALSE)


```
```{r}
summary_BHR_2018<-summary(PYRA.genidBHR2018)
summary_BHR_2018
mean(summary_BHR_2018$Hexp)
mean(summary_BHR_2018$Hobs)
t.test(summary_BHR_2018$Hobs, summary_BHR_2018$Hexp, paired = TRUE)
#PYRA.fstatSE2018
ARBHR18<-allelic.richness(PYRA.fstatBHR18)

summary(ARBHR18$Ar)
```
```{r}
summary_BH1_2018<-summary(PYRA.genidBH12018)
summary_BH1_2018
mean(summary_BH1_2018$Hexp)
mean(summary_BH1_2018$Hobs)
t.test(summary_BH1_2018$Hobs, summary_BH1_2018$Hexp, paired = TRUE)
ARBH118<-allelic.richness(PYRA.fstatBH118)
summary(ARBH118$Ar)
```
```{r}
summary_BH1_2019<-summary(PYRA.genidBH12019)
summary_BH1_2019
mean(summary_BH1_2019$Hexp)
mean(summary_BH1_2019$Hobs)
t.test(summary_BH1_2019$Hobs, summary_BH1_2019$Hexp, paired = TRUE)
ARBH119<-allelic.richness(PYRA.fstatBH119)
summary(ARBH119$Ar)
```
```{r}
summary_BH2_2018<-summary(PYRA.genidBH22018)
summary_BH2_2018
mean(summary_BH2_2018$Hexp)
mean(summary_BH2_2018$Hobs)
t.test(summary_BH2_2018$Hobs, summary_BH2_2018$Hexp, paired = TRUE)
ARBH218<-allelic.richness(PYRA.fstatBH218)
summary(ARBH218$Ar)
```
```{r}
summary_BH2_2019<-summary(PYRA.genidBH22019)
summary_BH2_2019
mean(summary_BH2_2019$Hexp)
mean(summary_BH2_2019$Hobs)
t.test(summary_BH2_2019$Hobs, summary_BH2_2019$Hexp, paired = TRUE)
ARBH219<-allelic.richness(PYRA.fstatBH219)
summary(ARBH219$Ar)
```
```{r}
summary_BHR_2019<-summary(PYRA.genidBHR2019)
summary_BHR_2019
mean(summary_BHR_2019$Hexp)
mean(summary_BHR_2019$Hobs)
t.test(summary_BHR_2019$Hobs, summary_BHR_2019$Hexp, paired = TRUE)
ARBHR19<-allelic.richness(PYRA.fstatBHR19)
summary(ARBHR19$Ar)
```

```{r}
summary_CBR_2018<-summary(PYRA.genidCBR2018)
summary_CBR_2018
mean(summary_CBR_2018$Hexp)
mean(summary_CBR_2018$Hobs)
t.test(summary_CBR_2018$Hobs, summary_CBR_2018$Hexp, paired = TRUE)
ARCBR18<-allelic.richness(PYRA.fstatCBR18)
summary(ARCBR18$Ar)
```
```{r}
summary_CBR_2019<-summary(PYRA.genidCBR2019)
summary_CBR_2019
mean(summary_CBR_2019$Hexp)
mean(summary_CBR_2019$Hobs)
t.test(summary_CBR_2019$Hobs, summary_CBR_2019$Hexp, paired = TRUE)
ARCBR19<-allelic.richness(PYRA.fstatCBR19)
summary(ARCBR19$Ar)
```
```{r}
summary_CB1_2018<-summary(PYRA.genidCB12018)
summary_CB1_2018
mean(summary_CB1_2018$Hexp)#0.73
mean(summary_CB1_2018$Hobs)#0.78
t.test(summary_CB1_2018$Hobs, summary_CB1_2018$Hexp, paired = TRUE)
ARCB118<-allelic.richness(PYRA.fstatCB118)
summary(ARCB118$Ar)
```
```{r}
summary_CB2_2018<-summary(PYRA.genidCB22018)
summary_CB2_2018
mean(summary_CB2_2018$Hexp)#0.73
mean(summary_CB2_2018$Hobs)#0.78
t.test(summary_CB2_2018$Hobs, summary_CB2_2018$Hexp, paired = TRUE)
ARCB218<-allelic.richness(PYRA.fstatCB218)
summary(ARCB218$Ar)
```
```{r}
summary_CB1_2019<-summary(PYRA.genidCB12019)
summary_CB1_2019
mean(summary_CB1_2019$Hexp)
mean(summary_CB1_2019$Hobs)
t.test(summary_CB1_2019$Hobs, summary_CB1_2019$Hexp, paired = TRUE)
ARCB119<-allelic.richness(PYRA.fstatCB119)
summary(ARCB119$Ar)
```

```{r}
summary_CB2_2019<-summary(PYRA.genidCB22019)
summary_CB2_2019
mean(summary_CB2_2019$Hexp)
mean(summary_CB2_2019$Hobs)
t.test(summary_CB2_2019$Hobs, summary_CB2_2019$Hexp, paired = TRUE)
ARCB219<-allelic.richness(PYRA.fstatCB219)
summary(ARCB219$Ar)
```
```{r}
summary_CB3_2019<-summary(PYRA.genidCB32019)
summary_CB3_2019
mean(summary_CB3_2019$Hexp)
mean(summary_CB3_2019$Hobs)
t.test(summary_CB3_2019$Hobs, summary_CB3_2019$Hexp, paired = TRUE)
ARCB319<-allelic.richness(PYRA.fstatCB319)
summary(ARCB319$Ar)
```

```{r}
t.test(summary_BHR_2018$Hobs, summary_BHR_2019$Hobs, paired = FALSE)
t.test(ARCB18$Ar, ARCBS19$Ar, paired = FALSE)#pvalue 0.87
t.test(ARCBS19$Ar, ARCB19$Ar, paired = FALSE)#pvalue 0.68
t.test(ARCB18$Ar, ARCB19$Ar, paired = FALSE)#pvalue 0.56
```
```{r}
t.test(summary_CB1_2018$Hobs, summary_CB2_2018$Hobs, paired = FALSE)#pvalue 0.91
t.test(summary_CB1_2019$Hobs, summary_CB2_2019$Hobs, paired = FALSE)#pvalue 0.76
t.test(summary_CB1_2019$Hobs, summary_CB3_2019$Hobs, paired = FALSE)#pvalue 0.99
t.test(summary_CB2_2019$Hobs, summary_CB3_2019$Hobs, paired = FALSE)#pvalue 0.78
t.test(summary_CBR_2018$Hobs, summary_CBR_2019$Hobs, paired = FALSE)#pvalue 0.30
```
```{r}
#LE Enclosure Comparisons
#NS differences from year to year with LE
t.test(summary_LE2012$Hobs, summary_LE2013$Hobs, paired = FALSE)#pvalue 0.09
t.test(summary_LE2013$Hobs, summary_LE2014$Hobs, paired = FALSE)#pvalue 0.43
t.test(summary_LE2014$Hobs, summary_LE2015$Hobs, paired = FALSE)#pvalue 0.27
t.test(summary_LE2015$Hobs, summary_LE2016$Hobs, paired = FALSE)#pvalue 0.21
t.test(summary_LE2016$Hobs, summary_LE2017$Hobs, paired = FALSE)#pvalue 0.08
t.test(summary_LE2017$Hobs, summary_LE2018$Hobs, paired = FALSE)#pvalue 0.51
t.test(summary_LE2012$Hexp, summary_LE2013$Hexp, paired = FALSE)#pvalue 0.94
t.test(summary_LE2013$Hexp, summary_LE2014$Hexp, paired = FALSE)#pvalue 0.62
t.test(summary_LE2014$Hexp, summary_LE2015$Hexp, paired = FALSE)#pvalue 0.60
t.test(summary_LE2015$Hexp, summary_LE2016$Hexp, paired = FALSE)#pvalue 0.64
t.test(summary_LE2016$Hexp, summary_LE2017$Hexp, paired = FALSE)#pvalue 0.32
t.test(summary_LE2017$Hexp, summary_LE2018$Hexp, paired = FALSE)#pvalue 0.09
t.test(ARLE12$Ar, ARLE13$Ar, paired = FALSE)#pvalue 0.40
t.test(ARLE13$Ar, ARLE14$Ar, paired = FALSE)#pvalue 0.35
t.test(ARLE14$Ar, ARLE15$Ar, paired = FALSE)#pvalue 0.69
t.test(ARLE15$Ar, ARLE16$Ar, paired = FALSE)#pvalue 0.67
t.test(ARLE16$Ar, ARLE17$Ar, paired = FALSE)#pvalue 0.02
t.test(ARLE17$Ar, ARLE18$Ar, paired = FALSE)#pvalue 8.59e-5
LE_AR<-c(9.81,8.88,9.99,9.51,9.05,11.71,7.16) #AR 9.44
LE_Ho<-c(0.76,0.81,0.83,0.80,0.76,0.82,0.79) #Ho 0.80
LE_He<-c(0.79,0.79,0.81,0.79,0.78,0.81,0.75) #He 0.79
mean(LE_Ho)
sd(LE_Ho)
mean(LE_He)
sd(LE_He)
mean(LE_AR)
sd(LE_AR)
```
```{r}
#SE Enclosure Comparisons
#NS differences from year to year with SE
t.test(summary_SE2012$Hobs, summary_SE2013$Hobs, paired = FALSE)#pvalue 0.47
t.test(summary_SE2013$Hobs, summary_SE2014$Hobs, paired = FALSE)#pvalue 0.92
t.test(summary_SE2014$Hobs, summary_SE2015$Hobs, paired = FALSE)#pvalue 0.53
t.test(summary_SE2015$Hobs, summary_SE2017$Hobs, paired = FALSE)#pvalue 0.85 - 2016 only contained a single indv.
t.test(summary_SE2017$Hobs, summary_SE2018$Hobs, paired = FALSE)#pvalue 0.41
t.test(summary_SE2012$Hexp, summary_SE2013$Hexp, paired = FALSE)#pvalue 0.99
t.test(summary_SE2013$Hexp, summary_SE2014$Hexp, paired = FALSE)#pvalue 0.73
t.test(summary_SE2014$Hexp, summary_SE2015$Hexp, paired = FALSE)#pvalue 0.001
t.test(summary_SE2014$Hexp, summary_SE2017$Hexp, paired = FALSE)#pvalue 0.02 - 2015, 2016 only contained a 1-2 indv.
t.test(summary_SE2017$Hexp, summary_SE2018$Hexp, paired = FALSE)#pvalue 0.004
t.test(summary_SE2014$Hexp, summary_SE2017$Hexp, paired = FALSE)#pvalue 0.02
t.test(ARSE12$Ar, ARSE13$Ar, paired = FALSE)#pvalue 0.82
t.test(ARSE13$Ar, ARSE14$Ar, paired = FALSE)#pvalue 0.82
t.test(ARSE14$Ar, ARSE17$Ar, paired = FALSE)#pvalue 0.0002
t.test(ARSE17$Ar, ARSE18$Ar, paired = FALSE)#pvalue 0.0003
SE_AR<-c(8.99,9.23,8.99,5.41,3.24) 
SE_Ho<-c(0.78,0.8,0.79,0.74,0.75,0.7) 
SE_He<-c(0.79,0.78,0.77,0.68,0.54) 
mean(SE_Ho)
sd(SE_Ho)
mean(SE_He)
sd(SE_He)
mean(SE_AR)
sd(SE_AR)
```
```{r}
#DE Enclosure Comparisons
#NS differences from year to year with DE EXCEPT FOR THE 1ST TO 2ND YEAR
t.test(summary_DE2013$Hobs, summary_DE2014$Hobs, paired = FALSE)#pvalue 0.04
t.test(summary_DE2014$Hobs, summary_DE2016$Hobs, paired = FALSE)#pvalue 0.64 - DE 2015 ONLY HAD A SINGLE INDIV.
t.test(summary_DE2016$Hobs, summary_DE2017$Hobs, paired = FALSE)#pvalue 0.60
t.test(summary_DE2017$Hobs, summary_DE2019$Hobs, paired = FALSE)#pvalue 0.93 - DE 2018 HAD A SINGLE INDV.
t.test(summary_DE2013$Hexp, summary_DE2014$Hexp, paired = FALSE)#pvalue 0.03
t.test(summary_DE2014$Hexp, summary_DE2016$Hexp, paired = FALSE)#pvalue 0.005 - DE 2015 ONLY HAD A SINGLE INDIV.
t.test(summary_DE2016$Hexp, summary_DE2017$Hexp, paired = FALSE)#pvalue 0.01
t.test(summary_DE2017$Hexp, summary_DE2019$Hexp, paired = FALSE)#pvalue 0.15 - DE 2018 HAD A SINGLE INDV.
t.test(ARDE13$Ar, ARDE14$Ar, paired = FALSE)#pvalue 0.02
t.test(ARDE14$Ar, ARDE16$Ar, paired = FALSE)#pvalue 3.45e-6
t.test(ARDE16$Ar, ARDE17$Ar, paired = FALSE)#pvalue 0.001
t.test(ARDE17$Ar, ARDE19$Ar, paired = FALSE)#pvalue 0.12
DE_AR<-c(6.47,8.35,4.02,6.53,5.39) 
DE_Ho<-c(.68,.74,.76,.74,.73) 
DE_He<-c(.7,.75,.66,.74,.69) 
mean(DE_Ho)
sd(DE_Ho)
mean(DE_He)
sd(DE_He)
mean(DE_AR)
sd(DE_AR)
```
```{r}
#BE Enclosure Comparisons
#NS differences from year to year with BE
t.test(summary_BE2014$Hobs, summary_BE2015$Hobs, paired = FALSE)#pvalue 0.91
t.test(summary_BE2015$Hobs, summary_BE2016$Hobs, paired = FALSE)#pvalue 0.24
t.test(summary_BE2016$Hobs, summary_BE2017$Hobs, paired = FALSE)#pvalue 0.29
t.test(summary_BE2014$Hexp, summary_BE2015$Hexp, paired = FALSE)#pvalue 0.72
t.test(summary_BE2015$Hexp, summary_BE2016$Hexp, paired = FALSE)#pvalue 0.61
t.test(summary_BE2016$Hexp, summary_BE2017$Hexp, paired = FALSE)#pvalue 0.94
t.test(ARBE14$Ar, ARBE15$Ar, paired = FALSE)#pvalue 0.24
t.test(ARBE15$Ar, ARBE16$Ar, paired = FALSE)#pvalue 0.41
t.test(ARBE16$Ar, ARBE17$Ar, paired = FALSE)#pvalue 0.60
BE_AR<-c(8.52,9.80,8.84,8.33) 
BE_Ho<-c(.79,.79,.74,.78) 
BE_He<-c(.77,.78,.76,.76) 
mean(BE_Ho)
sd(BE_Ho)
mean(BE_He)
sd(BE_He)
mean(BE_AR)
sd(BE_AR)
```
```{r}
#B2E Enclosure Comparisons
#S differences FROM 2017 (ALL ENLCLOSURE BORN) TO 2018 (MOSTLY WILD BORN), NS DIFFERENCE AFTER
t.test(summary_B2E2017$Hobs, summary_B2E2018$Hobs, paired = FALSE)#pvalue 0.003
t.test(summary_B2E2018$Hobs, summary_B2E2019$Hobs, paired = FALSE)#pvalue 0.74
```

```{r}
#ACROSS ENCLOSURES 2012
t.test(summary_LE2012$Hobs, summary_SE2012$Hobs, paired = FALSE) #pvalue 0.661
#ns differences in 2012
```
```{r}
#ACROSS ENCLOSURES 2013
t.test(summary_LE2013$Hobs, summary_SE2013$Hobs, paired = FALSE) #pvalue 0.66
t.test(summary_LE2013$Hobs, summary_DE2013$Hobs, paired = FALSE) #pvalue 0.0002
t.test(summary_SE2013$Hobs, summary_DE2013$Hobs, paired = FALSE) #pvalue 0.001
#s differences in 2013 between LE, SE with DE (initial year), ns between LE, SE
```
```{r}
#ACROSS ENCLOSURES 2014
t.test(summary_LE2014$Hobs, summary_SE2014$Hobs, paired = FALSE) #pvalue 0.31
t.test(summary_LE2014$Hobs, summary_DE2014$Hobs, paired = FALSE) #pvalue 0.0008
t.test(summary_LE2014$Hobs, summary_BE2014$Hobs, paired = FALSE) #pvalue 0.17
t.test(summary_SE2014$Hobs, summary_DE2014$Hobs, paired = FALSE) #pvalue 0.10
t.test(summary_SE2014$Hobs, summary_BE2014$Hobs, paired = FALSE) #pvalue 0.80
t.test(summary_DE2014$Hobs, summary_BE2014$Hobs, paired = FALSE) #pvalue 0.14
#s differences in 2014 between LE and DE (initial year), ns between other combinations
```
```{r}
#ACROSS ENCLOSURES 2015
t.test(summary_LE2015$Hobs, summary_SE2015$Hobs, paired = FALSE) #pvalue 0.49
t.test(summary_LE2015$Hobs, summary_BE2015$Hobs, paired = FALSE) #pvalue 0.77
t.test(summary_SE2015$Hobs, summary_BE2015$Hobs, paired = FALSE) #pvalue 0.56
#ns differences in 2015
```

```{r}
#ACROSS ENCLOSURES 2016
t.test(summary_LE2016$Hobs, summary_DE2016$Hobs, paired = FALSE) #pvalue 0.91
t.test(summary_LE2016$Hobs, summary_BE2016$Hobs, paired = FALSE) #pvalue 0.68
t.test(summary_DE2016$Hobs, summary_BE2016$Hobs, paired = FALSE) #pvalue 0.66
#ns differences in 2016
```

```{r}
#ACROSS ENCLOSURES 2017
t.test(summary_LE2017$Hobs, summary_SE2017$Hobs, paired = FALSE) #pvalue 0.22
t.test(summary_LE2017$Hobs, summary_DE2017$Hobs, paired = FALSE) #pvalue 0.05
t.test(summary_LE2017$Hobs, summary_BE2017$Hobs, paired = FALSE) #pvalue 0.29
t.test(summary_LE2017$Hobs, summary_B2E2017$Hobs, paired = FALSE) #pvalue 0.002

t.test(summary_SE2017$Hobs, summary_DE2017$Hobs, paired = FALSE) #pvalue 0.74
t.test(summary_SE2017$Hobs, summary_BE2017$Hobs, paired = FALSE) #pvalue 0.57
t.test(summary_SE2017$Hobs, summary_B2E2017$Hobs, paired = FALSE) #pvalue 0.003

t.test(summary_DE2017$Hobs, summary_BE2017$Hobs, paired = FALSE) #pvalue 0.24
t.test(summary_DE2017$Hobs, summary_B2E2017$Hobs, paired = FALSE) #pvalue 5.44e-5

t.test(summary_BE2017$Hobs, summary_B2E2017$Hobs, paired = FALSE) #pvalue 8.32e-5


#ns differences in 2017 between all combinations except for those with B2E (initial year, all indv taken from LE)

```
```{r}
#ACROSS ENCLOSURES 2018
t.test(summary_LE2018$Hobs, summary_SE2018$Hobs, paired = FALSE) #pvalue 0.19
t.test(summary_LE2018$Hobs, summary_B2E2018$Hobs, paired = FALSE) #pvalue 0.59
t.test(summary_SE2018$Hobs, summary_B2E2018$Hobs, paired = FALSE) #pvalue 0.44
#ns differences in 2018
```

```{r}
#ACROSS ENCLOSURES 2019
t.test(summary_DE2019$Hobs, summary_B2E2019$Hobs, paired = FALSE) #pvalue 1.00
```
```{r}
#Across years for B2E
t.test(summary_B2E2017$Hobs, summary_B2E2018$Hobs, paired = FALSE) #pvalue 0.004
t.test(summary_B2E2018$Hobs, summary_B2E2019$Hobs, paired = FALSE) #pvalue 0.74
t.test(summary_B2E2017$Hexp, summary_B2E2018$Hexp, paired = FALSE) #pvalue 0.005
t.test(summary_B2E2018$Hexp, summary_B2E2019$Hexp, paired = FALSE) #pvalue 0.39
t.test(ARB2E17$Ar, ARB2E18$Ar, paired = FALSE)#pvalue 3.45e-5
t.test(ARB2E18$Ar, ARB2E19$Ar, paired = FALSE)#pvalue 0.67
B2E_AR<-c(7.58,4.79,4.58) 
B2E_Ho<-c(.92,.75,.73) 
B2E_He<-c(.80,.69,.66) 
mean(B2E_Ho)
sd(B2E_Ho)
mean(B2E_He)
sd(B2E_He)
mean(B2E_AR)
sd(B2E_AR)

```
```{r}
library("adegenet")
library("hierfstat")
library("PopGenReport")
PYRA.genid_AR<-read.genepop("./CHAPTER 1 - FINAL/Genotypes_Allelic_Richness.gen")
PYRA.fstat_AR<-genind2hierfstat(PYRA.genid_AR)
PYRA_AR<-allelic.richness(PYRA.fstat_AR, diploid = TRUE, min.n = 10)
PYRA_AR
mean(PYRA_AR$Ar)
write.csv(PYRA_AR$Ar, file = "./CHAPTER 1 - FINAL/PYRA_AR.tsv")
```

